\documentclass[11pt, twocolumn]{article}
\usepackage{ amssymb }
\usepackage{fancyvrb}
\DefineVerbatimEnvironment{code}{Verbatim}{fontsize=\small}

\newcommand{\tab}{\hspace*{2em}}

\begin{document}
\title{Yippee: Web Search for the New Millenium}
\author{	TJ Du
	\and Chris Imbriano
	\and Margarita Miranda
	\and Nikos Vasilakis}
\date{April 2011}

\maketitle

\section{ Introduction }

To say the world wide web is enormous would be an understatement.  There are approximately 

\section{ High-level Approach }

The Yippee Search Engine will be comprised of 4 main components
\begin{itemize}
\item Web-crawler that will recursively download pages from the web
\item Indexer/TDF/IDF Retrieval Engine that will index relevant document features for later retrieval 
\item PageRank Calculations based on the Google PageRank description REFERENCE
\item Search Engine and User Interface
\end{itemize}

Most or all of the functionality of these components will be distributed among a number of nodes coordinated with the Pastry substrate.

\section{ Project Goals }

\subsection{ High Accuracy }
\subsection{ Crawler Efficiency }
\subsection{ Query Efficiency }

\section{ Milestones }

\subsection{Milestone 1}
First, we plan to create a complete map of our project architecture to ensure we
have a thoughtful design. Then, we will deploy minimally functioning
Pastry nodes locally and write the scripts to do so. Once that is
working, we will migrate those nodes to EC2. The web crawler will have a basic
implementation of pluggable components. The indexer will have a static lexicon
and all major components communicating with each other. 


\subsection{Milestone 2}
We will complete both the crawler and indexer and start these components on EC2
to begin building the corpus and index. 


\subsection{Milestone 3}
A basic PageRank Module should be created and working. We will create a wire
frame for the UI of our web application. For our final report, we will write a complete outline with finished report sections for the crawler
and indexer. 


\subsection{Milestone 4}
We will evaluate the performance of our PageRank and finish polishing the UI. 


\section{ Division of Labor }

While each member of the group is ultimately responsible for monitoring progress and completion of  one of the four components described in Section 2, no individual is tasked with its implementation.  Instead, the group collectively determines the high level architecture and component interfaces, then a pair of members breaks off to implement their assigned component. 

For the first milestone, Chris and Nikos will work on the Crawler and the preliminary components of FreePastry

 each component will be implemented by a pair of programmers.  So, once a high level architecture has been established by the group, the pair responsible ofr each component will break of and handle the imp



\section{References}

\begin{enumerate}
\item Reference 1
\item Reference 2
\item Reference 3
\end{enumerate}

\end{document}